\documentclass[a4paper,10pt]{article}

%A Few Useful Packages
\usepackage{marvosym}
\usepackage{tabularx}
\usepackage{fontspec} 					%for loading fonts
\usepackage{xunicode,xltxtra,url,parskip} 	%other packages for formatting
\RequirePackage{color,graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[big]{layaureo} 				%better formatting of the A4 page
% an alternative to Layaureo can be ** \usepackage{fullpage} **
\usepackage{supertabular} 				%for Grades
\usepackage{titlesec}					%custom \section

%Setup hyperref package, and colours for links
\usepackage{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

%FONTS
\defaultfontfeatures{Mapping=tex-text}
%\setmainfont[SmallCapsFont = Fontin SmallCaps]{Fontin}
%%% modified for Karol Kozioł for ShareLaTeX use
\setmainfont[
SmallCapsFont = Fontin-SmallCaps.otf,
BoldFont = Fontin-Bold.otf,
ItalicFont = Fontin-Italic.otf
]
{Fontin.otf}
%%%

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{3pt}{3pt}
%Tweak a bit the top margin
%\addtolength{\voffset}{-1.3cm}

%Italian hyphenation for the word: ''corporations''
\hyphenation{im-pre-se}

%-------------WATERMARK TEST [**not part of a CV**]---------------
\usepackage[absolute]{textpos}

\setlength{\TPHorizModule}{30mm}
\setlength{\TPVertModule}{\TPHorizModule}
\textblockorigin{2mm}{0.65\paperheight}
\setlength{\parindent}{0pt}

%--------------------BEGIN DOCUMENT----------------------
\begin{document}

%WATERMARK TEST [**not part of a CV**]---------------
%\font\wm=''Baskerville:color=787878'' at 8pt
%\font\wmweb=''Baskerville:color=FF1493'' at 8pt
%{\wm 
%	\begin{textblock}{1}(0,0)
%		\rotatebox{-90}{\parbox{500mm}{
%			Typeset by Alessandro Plasmati with \XeTeX\  \today\ for 
%			{\wmweb \href{http://www.aleplasmati.comuv.com}{aleplasmati.comuv.com}}
%		}
%	}
%	\end{textblock}
%}

\pagestyle{empty} % non-numbered pages

\font\fb=''[cmr10]'' %for use with \LaTeX command

%--------------------TITLE-------------
\par{\centering
		{\Huge Osama   \textsc{Mohsen}
	}\bigskip\par}

%--------------------SECTIONS-----------------------------------
%Section: Personal Data
\section{Personal Data}

\begin{tabular}{rl}
    \textsc{Address:}  &  Chicago, Illinois, USA \\
    \textsc{Phone:}     & +1 815 9952126\\
    \textsc{email:}     & \href{mailto:omohsen@niu.edu}{osama.emohsen@gmail.com}
\end{tabular}


%Section: Education
\section{Education}
\begin{tabular}{rl}	
2016 - 2021  & Doctor of Philosophy in \textsc{Physics}, \small \textbf{Northern Illinois University}, Dekalb, IL, USA\\
& Advisor: Prof. \textit{ Philippe Piot} \\
\vspace{0.1cm} \\
2012 - 2015& Master of Science in \textsc{Physics}, , \small \textbf{University of Jordan.} Amman, Jordan\\ 
&  Advisor: Prof. \textit{Sami Mahmood}\\
\vspace{0.1cm} \\
2007 - 2012 & Bachelor of Science in \textsc{Applied Physics} \small \textbf{Jordan Uni. of Science and Technology}, 
\\ & Irbid, Jordan \\

\end{tabular}

%Section: Work Experience at the top
\section{Work Experience}
\begin{tabular}{r|p{11cm}}
\textsc{2021-\hspace{0.7cm}} & Postdoctoral Research Associate,  \small \textsc{Fermi national laboratory} \\
&\emph{Instabilities in intense hadron beams }\\
\\
\textsc{2016-2021} & Graduate Research Assistant, \small \textsc{Northern Illinois University} \\
 &\emph{High Brightness Electron Sources and their Applications}\\
 \\
 \textsc{2012- 2015} & Graduate Research Assistant, \small \textsc{University of Jordan}  \\
&\emph{Structural Analysis of Y- and W-Type Hexaferrites}\\
\end{tabular}


\section{Awards}
Thesis completion fellowship, 2020-2021
%Section: Scholarships and additional info
\section{Non Academic Experience}
\begin{tabular}{rll}

 2019- & 2021& Member, Graduate Student Colloquium Committee \\
 2018-&2019 & Representative, Graduate Student Advisory Committee (GSAC) \\
 2017-&2019 & Secretary and Co-founder, Physics Graduate Student Association (PGSA) \\

\end{tabular}

%Section: Languages
\section{Languages}
\begin{tabular}{rl}
 \textsc{Arabic:}&Mothertongue\\
\textsc{English:}&Fluent\\
\end{tabular}

\section{Computer Skills}
\begin{tabular}{rl}
Basic Knowledge:& \textsc{Linux}, \textsc{C++}, \textsc{Bash} \\
Intermediate Knowledge:& \textsc{Python}\\
Beam Physics codes: & \textsc{Impact-T, Astra, WARP, SPIFFE, Elegant, ACE3p,SUPERFISH}
\end{tabular}


\section{Courses and Certificates}
\begin{tabular}{lll}
U.S. Particle Accelerator School & Simulation of Beam and Plasma Systems &  2018 \\
U.S. Particle Accelerator School & 	Beam Physics with Intense Space Charge &  2017 \\
Joint Universities Accelerator School & The science of particle accelerators & 2016 \\
\end{tabular}


\section{References}

\begin{tabularx}{\textwidth}{X X}
    Prof. Philippe Piot  &  \href{mailto:piot@nicadd.niu.edu}{piot@nicadd.niu.edu} \\
    Dr. Jayakar C. Thangaraj  & \href{mailto:jtobin@fnal.gov}{jtobin@fnal.gov} \\
    Dr. Giorgio Paolucci &  
    \href{mailto:giorgio.paolucci@elettra.eu}{giorgio.paolucci@elettra.eu} \\
    
    Prof. Sami Mahmood & \href{mailto:s.mahmood@ju.edu.jo}{s.mahmood@ju.edu.jo}\\
    \end{tabularx}
\newpage
\section{Publications and Proceedings}

\textbf{Mohsen, O.}, Mihalcea, D., Tom, N., Adams, N., Dhuley, R. C., Geelhoed, M. I., \& Xu, T. (2021). A field-enhanced conduction-cooled superconducting cavity for high-repetition-rate ultrafast electron bunch generation. Nuclear Instruments and Methods in Physics Research Section A: Accelerators, Spectrometers, Detectors and Associated Equipment, 1005, 165414. \\

\textbf{Mohsen, O.}, Divan, R., Korampally, V., Lueangaramwong, A., Piot, P., Sumant, A., \& Valluri, S. (2019, June). \textit{Performances of Silicon-Based Field-Emission Cathodes Coated with UltraNano Crystalline Diamond}. In 10th Int. Partile Accelerator Conf.(IPAC'19), Melbourne, Australia, 19-24 May 2019 (pp. 2117-2120). JACOW Publishing, Geneva, Switzerland.\\

\textbf{Mohsen, O.}, McKeown, A., Mihalcea, D., Dhuley, R. C., Geelhoed, M. I., Korampally, V., \& Thangaraj, J. C. T. (2019, June). \textit{Simulations and Experimental Plans for a High-Repetition-Rate Field-Enhanced Conduction-Cooled Superconducting RF Electron Source}. In 10th Int. Partile Accelerator Conf.(IPAC'19), Melbourne, Australia, 19-24 May 2019 (pp. 2113-2116). JACOW Publishing, Geneva, Switzerland.

Lueangaramwong, A., \textbf{Mohsen, O.}, \& Piot, P. (2018, August). \textit{Design of the Low-energy DC Gun for Field-emission Cathode Investigation}. In 2018 IEEE Advanced Accelerator Concepts Workshop (AAC) (pp. 1-4). IEEE. \\

\textbf{Mohsen, O.} , Lueansaramwong, A., Valluri, S., Korampally, V., Piot, P., \& Chattopadhyay, S. (2018, August). \textit{Field Emission from Silicon Nanocones Cathodes}. In 2018 IEEE Advanced Accelerator Concepts Workshop (AAC) (pp. 1-5). IEEE. \\

\textbf{Mohsen, O.}, Gonin, I., Kephart, R., Khabiboulline, T., Piot, P., Solyak, N., ... \& Yakovlev, V. (2018). \textit{Initial beam dynamics simulations of a high-average-current field-emission electron source in a superconducting radiofrequency gun}. Nuclear Instruments and Methods in Physics Research Section A: Accelerators, Spectrometers, Detectors and Associated Equipment. \\


Mahmood, S. H., Al Sheyab, Q., Bsoul, I., \textbf{ Mohsen, O.}, \& Awadallah, A. (2018). \textit{Structural and magnetic properties of Ga-substituted Co2− W hexaferrites}. Current Applied Physics, 18(5), 590-598. \\

Alhwaitat, E. S., Mahmood, S. H., Al-Hussein, M., \textbf{Mohsen, O.} E., Maswadeh, Y., Bsoul, I., \& Hammoudeh, A. (2018). \textit{Effects of synthesis route on the structural and magnetic properties of Ba3Zn2Fe24O41 (Zn2Z) nanocrystalline hexaferrites}. Ceramics International, 44(1), 779-787. \\

Lueangaramwong, A., Buzzard, C., Chattopadhyay, S., Divan, R., Korampally, V., \textbf {Mohsen, O.}, \& Piot, P. (2017, May). \textit{Experimental Investigation of Field-Emission From Silicon Nano-Cone Cathodes}. In 8th Int. Particle Accelerator Conf.(IPAC'17), Copenhagen, Denmark, 14â 19 May, 2017 (pp. 548-550). JACOW, Geneva, Switzerland. \\

\textbf{Mohsen, O.}, Mahmood, S. H., Awadallah, A., \& Maswadeh, Y. (2017). \textit{Effect of heat treatment on the structural and microstructural properties of the Co2-Y hexaferrites}. arXiv preprint arXiv:1709.02964. \\


Mahmood, S. H., Zaqsaw, M. D., \textbf{Mohsen, O. E.}, Awadallah, A., Bsoul, I., Awawdeh, M., \& Mohaidat, Q. I. (2015). \textit{Modification of the Magnetic Properties of Co2Y Hexaferrites by Divalent and Trivalent Metal Substitutions}. Solid State Phenomena, 241, 93–125.


\end{document}

